(Working Title) Properties of the \KT\ Campaign 1 Planets, False Positive Probabilities, and Confirmation of $N$ Systems. You Were Warned: it's a Working Title.

### 2015-03-02 ms.tex
testing pdflscape
Apparently revtex4.1 doesn't play well with pdflscape...

\bibliographystyle{apj}
\usepackage{subfigure}
\usepackage{url}
\usepackage{hyperref}
\usepackage{datetime}
\usepackage{longtable}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{ulem}
\usepackage{bm}
\usepackage[usenames,dvipsnames]{xcolor}

@@

\begin{document}
\title{(Working Title) Properties of the \KT\ Campaign 1 Planets, 
False Positive Probabilities, and Confirmation of $N$ Systems. You 
Were Warned: it's a Working Title.}

@@

With the exception of one star in our sample (EPIC 201912552), we do not have
spectroscopic data with which to characterize the stellar properties. 
Instead, we rely on photometry.
For each system, we query the VizieR database of astronomical catalogues
\citep{Ochseinbein00}. 
We record the $B$, $V$, $g'$, $r'$, and $i'$ magnitudes and their
uncertainties from the AAVSO Photometric all-sky survey (APASS) DR6 
\btmtodo{Cite: Who?}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
We also record the $J$, $H$, and $K$ magnitudes and their uncertainties 
as found in the 2MASS All-Sky Catalog of Point Sources \citep{Cutri03}
and the four WISE magnitudes and uncertainties from the ALLWise Data
Release \citep{Cutri13}.
For all except two of our targets, the $W4$ band is only an upper limit.
These data are reported in Table \ref{Tab:Photometry}.

@@

@@

We observed EPIC 201912552 on (all UT) February 04 2015, February 24 2015,
and February \btmtodo{XX} 2015 with the Tillinghast Reflector Echelle
Spectrograph (TRES) on the 1.5 m Tillinghast Reflector at the Fred L.
Whipple Observatory. 
The spectra were taken with a resolving power of $R=44,000$ and 
integration times ranging from 2800 to 3600 seconds, resulting in 
signal-to-noise ratios between 17 and 29 per resolution element.

\anytodo{This will be text from DaveL and/or Allyson Bieryla.}

@@

>>>>

\bibliographystyle{apj}
\usepackage{subfigure}
\usepackage{url}
\usepackage{hyperref}
\usepackage{datetime}
\usepackage{longtable}
%\usepackage{lscape}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{ulem}
\usepackage{bm}
\usepackage[usenames,dvipsnames]{xcolor}

@@

\begin{document}

\title{(Working Title) Properties of the \KT\ Campaign 1 Planets, 
False Positive Probabilities, and Confirmation of $N$ Systems. You 
Were Warned: it's a Working Title.}

@@

With the exception of one star in our sample (EPIC 201912552), we do not have
spectroscopic data with which to characterize the stellar properties. 
Instead, we rely on photometry.
For each system, we query the VizieR database of astronomical catalogues
\citep{Ochseinbein00}. 
We record the $B$, $V$, $g'$, $r'$, and $i'$ magnitudes and their
uncertainties from the AAVSO Photometric all-sky survey (APASS) DR6 
\btmtodo{Cite: Who?}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
We also record the $J$, $H$, and $K$ magnitudes and their uncertainties 
as found in the 2MASS All-Sky Catalog of Point Sources \citep{Cutri03}
and the four WISE magnitudes and uncertainties from the ALLWise Data
Release \citep{Cutri13}.
For all except two of our targets, the $W4$ band is only an upper limit.
These data are reported in Table 1.

@@

The full list of stellar parameters adopted in this paper is included in
Table 2.
% For some reason I can't get it to identify the table \ref here. 
% If anyone can figure it out, be my guest!

@@

We observed EPIC 201912552 on (all UT) February 04 2015, February 24 2015,
and February \btmtodo{XX} 2015 with the Tillinghast Reflector Echelle
Spectrograph (TRES) on the 1.5 m Tillinghast Reflector at the Fred L.
Whipple Observatory. 
These dates were chosen to be near the times of largest RV variations, 
corresponding to phases of \btmtodo{PHASES} relative to the time
of transit.
The spectra were taken with a resolving power of $R=44,000$ and 
integration times ranging from 2800 to 3600 seconds, resulting in 
signal-to-noise ratios between 17 and 29 per resolution element.

The spectra were extracted as described in \citet{Buchhave10}. 
The relative RVs were derived by cross-correlating the spectra against the
strongest observed spectrum (in this case, the first) over the wavelength
range 4700 - 6800 Angstroms. 
We selected 19 echelle orders in the analysis, being careful to reject
orders with telluric absorption lines, fringing in the far red and those
with very low SNR in the blue.

The two observed spectra have RVs that differ by $47.1 \pm xx.x$ m s$^{-1}$.
A deviation at this magnitude can only be explained by the presence of 
a planetary system and instrumental noise, eliminating the possibility the
transiting planet is actually a false positive.

@@

\include{table_photometry}

\include{table_stellarprops}
